Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-07 R/model_persistence_check.Rmd
Update model_persistence_check.Rmd

```{r load-models, collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_persistence_2.Rdata"))
load(file = here("outputs", "models", "model_persistence_full.Rdata"))
# BARG 1.E
#load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
# BARG 5.A/B/C
#load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
m_1 <- m2
m_2 <- m_full
```

>>>>

```{r load-models, collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_persistence_2.Rdata"))
#load(file = here("outputs", "models", "model_persistence_full.Rdata"))
# BARG 1.E
load(file = here("outputs", "models", "model_persistence_2_prior.Rdata"))
# BARG 5.A/B/C
#load(file = here("outputs", "models", "model_persistence_2_flat.Rdata"))
m_1 <- m2
#m_2 <- m_full
m_2 <- m2_prior
```
